---
title: "WORMS_get_trait_data"
author: "Nathan R. Geraldi"
date: "April 25, 2022"
output: github_document
---

set table options
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## libraries
```{r libraries, message=FALSE, warning=FALSE}

library(fields)
library(psych)
library(tidyverse) 

library(worrms) # used but not loaded  devtools::install_github("ropensci/worrms")
```

## functions
```{r functions, message=FALSE, warning=FALSE}
# function to remove rows with n number of NA's
delete.na <- function(DF, n=0) {
  DF[rowSums(is.na(DF)) <= n,]
}
  ######################################################################
  
#' Function to get functional group info for an Aphia ID
#### from --   https://github.com/tomjwebb/WoRMS-functional-groups
#  didn't use, removed  get_worms_fgrp

  


```


## define universal variables
```{r define_universal}


dir<-"/Users/nathangeraldi/Dropbox/"
out_file<-"Documents/Naturemetrics/data/worms_traits/"
# export  to project folder
export_file<-out_file
#  name of data
dat_name<-paste("SOTEAG Appendices.xlsx")  
# name for dating info


############
################### set file path and name of sample data
sam_file_path<-paste0(dir,out_file,dat_name) ## set sample data file

##

```


## import data
Sample data excel sheet see post_DADA2 rmd for details
```{r import}
# sample data -- will need Quality control !!! make sure sample_se make sense
sheets <- openxlsx::getSheetNames(sam_file_path)
sam_dat <- lapply(sheets,openxlsx::read.xlsx,xlsxFile=sam_file_path)  # mes1<-sam_dat[[2]]   names(mes1)  names(sam_dat)
names(sam_dat) <- sheets   # add name to each list

# bind if mutliple sheets
dat<-bind_rows(sam_dat, .id = 'type') 
 mes<-sam_dat[[1]]

```


## tidy species


```{r tidy_sp}
# tidy     names(dat)   names(taxa)
tl<-c("Superkingdom","Kingdom","Phylum", "Class", "Order", "Family", "Genus", "Species")  # set for separate lineage
tl<-c("Kingdom","Phylum", "Class", "Order", "Family", "Genus", "Species")  # set for separate lineage

taxa<- dat %>% # names(dat)   unique(dat$primer)   unique(taxa$primer)
    select(Kingdom,Phylum, Class, Order, Family, Genus, Species) %>% 
    unite("lineage", Kingdom:Species, sep=";") %>% 
    filter(!duplicated(lineage)) %>% # remove duplicate species
    tidyr::separate(lineage, into=tl, sep=";" , remove=FALSE)   %>% 
   #mutate(Species_clean=gsub("(sp. ).*", "\\1", Species)  ) %>%  # clean names remove everything after sp. in speceis 
   # mutate(Species_clean=gsub("[", "", Species_clean, fixed = TRUE)  ) %>% 
   # mutate(Species_clean=gsub("]", "", Species_clean, fixed = TRUE)  ) %>% 
  # remove white space, just in case
    mutate(Species=trimws(Species))
    
  ##  remove taxa without species
taxa2<- taxa %>%
      filter(Species!="NA")
```


## export
turned off
```{r export}

#  data.table::fwrite(taxa,paste(dir,export_file,"Red_sea_eDNA_taxa_v2.csv",sep=""),row.names=F, sep=",")

```




## worm info
use worms package to get accepted names
use warms package to get information including - Kingdom through species
```{r worms_info}
##   check and change names in worms     ##################################
#   library(worrms)
### test
xx<-taxa2$Species[1:5] # set species name column
sp_info <- worrms::wm_records_names(name = xx, fuzzy = F, marine_only = F) # get worrms info
worm_info <- bind_rows(sp_info)    #  make dataframe,   names(my_sp_taxo)

#####   begin loop to get basic worrms info -- 
# set pattern
xx<-taxa2$Species # set species name column
z<-50  ## batch size
stt<-seq(1,length(xx),by=z)  # head(stt)   

for (i in stt) {
  
  if (i== last(stt)){
    j<-length(xx) } else{j<-i+(z-1)}

g<- xx[i:j]
gg <- worrms::wm_records_names(name = g, fuzzy = F, marine_only = F) # get worrms info
ggg<-bind_rows(gg) 

if (i==1){
  worm_info<-ggg}
else{
  worm_info<-rbind(worm_info,ggg)}
print(j)  # print(Sys.time()) 
}

## tidy
#   names(worm_info)
worm_info <- worm_info %>% 
  select(AphiaID, scientificname, valid_AphiaID, valid_name, kingdom, phylum, class, order, family, genus, isMarine) %>% 
  rename(AphiaID_old = AphiaID, species_ncbi = scientificname, AphiaID = valid_AphiaID,  species_worrms=valid_name )

```

## worm attributes
get size and
```{r worms_attt1}
## use aphid id to get more info
## basics
#
#   at<-  worrms::wm_attr_data(id = 494981)  #sp_info$AphiaID[8])


xx<-worm_info$AphiaID[complete.cases(worm_info$AphiaID)] # set species name column
xx<- xx[!duplicated(xx)]## remove dups, just in case corrections made them
z<-50  ## batch size
stt<-seq(1,length(xx),by=z)  # head(stt)   i<-1;j<-50

for (i in stt) {
  
  if (i== last(stt)){
    j<-length(xx) } else{j<-i+(z-1)}

g<- xx[i:j]
gg <- worrms::wm_attr_data_(id = g, include_inherited=TRUE) # get worrms info
ggg<-bind_rows(gg) 

if (i==1){
  worm_att1<-ggg}
else{
  worm_att1<-rbind(worm_att1,ggg)}
print(j)  # print(Sys.time()) 
}


```

## tidy attributts
get size and
```{r tid_attt1}
## tidy       
  worm_att1_2<- worm_att1 %>%     # names(worm_att1_2)    unique(worm_att1_2$measurementType)
    separate(children, into=letters[1:10], sep=",") %>% ## get extra info including unit - mm or cm
    select(AphiaID, measurementType, measurementValue, c, d, AphiaID_Inherited, source_id) %>% 
    mutate(c=qdapRegex::rm_between(c, '"', '"', extract=TRUE)) %>% 
    mutate(d=qdapRegex::rm_between(d, '"', '"', extract=TRUE))  %>% 
    mutate(c=unlist(c), d=unlist(d)) %>% 
    rename( measure_defn= c, unit = d) %>% 
          ungroup()  %>% 
      mutate(AphiaID = as.numeric(AphiaID))
  
## body size
  worm_att1_bs <- worm_att1_2 %>%   # unique(worm_att1_bs$unit)
      filter(measurementType == "Body size (qualitative)" | measurementType == "Body size") %>% # check if qualitative - all 0.2-200 mm
      mutate(size_mm = -100) %>% 
      mutate(size_mm = if_else(unit=="mm" , as.numeric(measurementValue), size_mm)) %>% 
      mutate(size_mm = if_else(unit=="µm" , as.numeric(measurementValue)/1000, size_mm)) %>% 
    # switched from *1000 to /1000 and /10 to *10 in May 2022 an reran !!!!!!!!
      mutate(size_mm = if_else(unit=="cm" , as.numeric(measurementValue)*10, size_mm))  %>%
    mutate(size_mm = replace(size_mm, size_mm<0, NA)) %>% 
      select(-measurementType) %>% 
      group_by(AphiaID) %>% 
      summarize(max_size_mm= max(size_mm, na.rm = TRUE)) %>% 
      select(AphiaID, max_size_mm) %>% 
      rename( max_body_size_mm = max_size_mm) 

  
## Functional group
    worm_att1_fg <- worm_att1_2 %>%   # unique(worm_att1_bs$unit)    names(worm_att1_fg )
      filter(measurementType == "Functional group") %>%
      select(AphiaID, measurementValue, unit) %>% 
      mutate(unit = if_else(unit=="larva > planula" , "larva_planula" , unit))  %>%  # fix so good column name
      distinct() %>% ## remove duplicate rows
      ## add fixes for error mentioned in next note
      filter( ! (AphiaID==103862 & measurementValue == "benthos > macrobenthos") ) %>%  # keep only benthos
      filter( ! (AphiaID==112849 & measurementValue == "benthos > meiobenthos") ) %>%  # keep only benthos
      filter( ! (AphiaID==115723 & measurementValue == "benthos > meiobenthos") ) %>%  # keep only benthos
      filter( ! (AphiaID==115960 & measurementValue == "benthos > meiobenthos") ) %>%  # keep only benthos
      filter( ! (AphiaID==136084 & measurementValue == "benthos > macrobenthos") ) %>%  # keep only benthos
      filter( ! (AphiaID==355663 & measurementValue == "plankton > mesoplankton") ) %>%  # keep only bentho
      filter( ! (AphiaID==  410749 & measurementValue == "benthos > meiobenthos") ) %>%  # keep only benthos
       filter( ! (AphiaID==  206950 & measurementValue == "plankton > mesoplankton") ) %>%  # keep only benthos
    filter( ! (AphiaID==  206952 & measurementValue == "plankton > mesoplankton") ) %>%  # keep only benthos
    filter( ! (AphiaID==  207211 & measurementValue == "plankton > mesoplankton") ) %>%  # keep only benthos
    filter( ! (AphiaID==  220588 & measurementValue == "benthos > macrobenthos") ) %>%  # keep only benthos
    filter( ! (AphiaID== 231751 & measurementValue == "benthos > macrobenthos") ) %>%  # keep only benthos
   filter( ! (AphiaID== 110303 & measurementValue == "mixoplankton > Constitutive Mixoplankton") ) %>%  # keep only benthos
      filter( ! (AphiaID== 234031 & measurementValue == "benthos > epibenthos") ) %>%  # keep only benthos
    filter( ! (AphiaID== 427742 & measurementValue == "plankton > microplankton") ) %>%  # keep only benthos
     filter( ! (AphiaID== 663583 & measurementValue == "plankton > nanoplankton") ) %>%  # keep only benthos
      
      # may get error in this line, rerun up to here and then look at duplicate errors and fix
      spread(key=unit,value=measurementValue, fill=NA) %>% 
      mutate(adult = if_else(polyp=="benthos" , polyp , adult, adult))  %>%
     # mutate(larva = if_else(complete.cases(nauplius) , nauplius , larva, larva))  %>%
      mutate(larva = if_else(complete.cases(larva_planula) , larva_planula , larva, larva))  %>%
      select(AphiaID, adult, larva) %>% 
      rename( functinoal_group_adult = adult , functinoal_group_larva = larva )
  
## "Feedingtype"
      worm_att1_ft <- worm_att1_2 %>%   #   unique(worm_att1_ft$feeding_type)
          filter(measurementType == "Feedingtype") %>% 
          filter(unit!="larva" |  is.na(unit)) %>% 
          select(AphiaID, measurementValue) %>% 
          rename( feeding_type = measurementValue ) %>% 
          mutate(ft2 = if_else(grepl("deposit",feeding_type ) , "deposit feeder" , feeding_type)) %>% 
          mutate(ft2 = if_else(grepl("parasitic",ft2) , "parasitic" , ft2)) %>% 
        mutate(ft2 = if_else(grepl("carnivore",ft2) , "predator" , ft2)) %>% 
        mutate(ft2 = if_else(grepl("grazer",ft2) , "grazer" , ft2)) %>% 
        mutate(ft2 = if_else(grepl("suspension",ft2) , "suspension or filter feeder" , ft2)) %>% 
        mutate(ft2 = if_else(grepl("filter",ft2) , "suspension or filter feeder" , ft2)) %>%
        ## duplicates need specific
        mutate(ft2 = if_else( AphiaID==413379 , "grazer" , ft2)) %>% #molusk that grazes algae - more than deposit feeder
        mutate(ft2 = if_else( AphiaID==207675 , "suspension or filter feeder" , ft2)) %>% # giant clam - bivalve more associated with filter than symbiont
        mutate(ft2 = if_else( AphiaID==106623 , "parasitic" , ft2)) %>% 
        
        select(AphiaID,ft2) %>% 
        rename(feeding_type = ft2) %>% 
            distinct(AphiaID, .keep_all = TRUE )  #   %>% # will take alphabetically first entry - favors predator over scavenger!!!!!!
     
         # filter(duplicated(AphiaID))  
      # !!!  to check each time !!!  , shouldn't be any dups if yes then remove at if_else and aphid id
       mes<-worm_att1 %>% 
         filter(AphiaID==106623)


## AMBI ecological group
          worm_att1_AMBI <- worm_att1_2 %>%   # 
          filter(measurementType == "AMBI ecological group")
      ##      ONLY 46 - do not use yet


####    add back to original worrm data
 
          worm_info2 <- worm_info %>%     
              left_join(worm_att1_bs) %>% 
            left_join(worm_att1_fg) %>% 
            left_join(worm_att1_ft) %>% 
            rename(species_clean_ncbi = species_ncbi, AphiaID_ncbi=AphiaID_old)
##    !!!!!!  make sure has same number of rows as worm_info !!!!! -- ****will need to fix*****  !!!!!!!!!!!!!!
          
```


## combine 
add back to original taxonomy table
```{r combine}
#  names(taxa)  names(worm_info2)    names(taxa2)

taxa2 <- taxa %>% 
  rename(species_clean_ncbi = Species) %>% 
  left_join(worm_info2) 
  

```





## export
```{r export}
data.table::fwrite(worm_info2,paste(dir,export_file,"Soteag_sizes_worms.csv",sep=""),row.names=F, sep=",")


data.table::fwrite(taxa2,paste(dir,export_file,"Soteag_sizes_worms.csv",sep=""),row.names=F, sep=",")

# to shared folder
data.table::fwrite(taxa2,paste(dir,share_file,"Red_sea_eDNA_traits2_v2.csv",sep=""),row.names=F, sep=",")
```




## compare versoins - 1
April 2021 re-ran tax assign, changed taxonomy
need to combine and check
```{r compare}

#  dat_new<-data.table::fread(file = paste0(dir,share_file,"Red_sea_eDNA_traits2_v2.csv"),sep=",")
dat_new<-data.table::fread(file = paste(dir,export_file,"Red_sea_eDNA_taxa_v2.csv",sep="") , sep=",")# only 18s but no worrms traits

dat_orig<- openxlsx::read.xlsx(xlsxFile= paste0(dir,share_file,"Red_sea_eDNA_traits_Ken2.xlsx")   )
colnames(dat_orig)[25]<-"AS_worms"

dat2<-dat_orig %>%  # names(dat)
    distinct(lineage, .keep_all = FALSE)

new2<-dat_new %>% 
  distinct(lineage, .keep_all = TRUE) 




```



## fix old ver
use same changes used to fix to fix old
```{r fix old}


dat2<-dat_orig %>%  # names(dat_orig)
    distinct(lineage, .keep_all = TRUE) %>%
  select(lineage:Species, isMarine:X42) %>% 
  rename(kingdom=Kingdom, phylum=Phylum, class=Class, order=Order, family=Family, genus=Genus) %>% 
#
#
 mutate( kingdom=if_else (kingdom=="Metazoa",  "Animalia" , kingdom )  ) %>% 
  mutate( class=if_else (class=="Dinoflagellata incertae sedis",  "Dinophyceae" , class )  ) %>% 
  mutate( order=if_else (order=="Gymnodiniaceae",  "Gymnodiniales " , order )  ) %>% 
   mutate( phylum=if_else (class=="Dinophyceae",  "Myzozoa" , phylum )  ) %>% 
  mutate( kingdom=if_else (class=="Dinophyceae",  "Chromista" , kingdom )  ) %>% 
  mutate( phylum=if_else (class=="Dictyochophyceae",  "Ochrophyta" , phylum )  ) %>% 
  mutate( kingdom=if_else (class=="Dictyochophyceae",  "Chromista" , kingdom )  ) %>% 
mutate( phylum=if_else (class=="Ichthyosporea",  "Choanozoa" , phylum )  ) %>% 
  mutate( kingdom=if_else (class=="Ichthyosporea",  "Protozoa" , kingdom )  ) %>% 
  mutate( phylum=if_else (class=="Chrysophyceae",  "Ochrophyta" , phylum )  ) %>% 
  mutate( kingdom=if_else (class=="Chrysophyceae",  "Chromista" , kingdom )  ) %>%
  mutate( phylum=if_else (class=="Pelagophyceae",  "Ochrophyta" , phylum )  ) %>% 
  mutate( kingdom=if_else (class=="Pelagophyceae",  "Chromista" , kingdom )  ) %>% 
   mutate( phylum=if_else (class=="Phaeophyceae",  "Ochrophyta" , phylum )  ) %>% 
  mutate( kingdom=if_else (class=="Phaeophyceae",  "Chromista" , kingdom )  ) %>% 
   mutate( kingdom=if_else (phylum=="Rhodophyta",  "Plantae" , kingdom )  ) %>% # Rhodophyta
  mutate( kingdom=if_else (kingdom=="Viridiplantae",  "Plantae" , kingdom )  ) %>%
  mutate( class=if_else (order=="Thraustochytrida",  "Labyrinthulea" , class )  ) %>% 
  mutate( phylum=if_else (order=="Thraustochytrida",  "Bigyra" , phylum )  ) %>% 
  mutate( kingdom=if_else (order=="Thraustochytrida",  "Chromista" , kingdom )  ) %>% 
  mutate( class=if_else (order=="Labyrinthulida",  "Labyrinthulea" , class )  ) %>% 
  mutate( phylum=if_else (order=="Labyrinthulida",  "Bigyra" , phylum )  ) %>% 
  mutate( kingdom=if_else (order=="Labyrinthulida",  "Chromista" , kingdom )  ) %>% 
  mutate( class=if_else (order=="Bicosoecida",  "" , class )  ) %>% 
  mutate( phylum=if_else (order=="Bicosoecida",  "Bigyra" , phylum )  ) %>% 
  mutate( kingdom=if_else (order=="Bicosoecida",  "Chromista" , kingdom )  ) %>% 
   mutate( class=if_else (order=="Chaetonotida",  "" , class )  ) %>% 
  mutate( phylum=if_else (order=="Chaetonotida",  "Gastrotricha" , phylum )  ) %>% 
  mutate( kingdom=if_else (order=="Chaetonotida",  "Animalia" , kingdom )  ) %>% 
mutate( kingdom=if_else (phylum=="Apicomplexa",  "Chromista" , kingdom )  ) %>% 
mutate( class=if_else (class=="Coscinodiscophyceae",  "Bacillariophyceae" , class )  ) %>% 
mutate( phylum=if_else (phylum=="Bacillariophyta",  "Bacillariophyceae" , phylum )  ) %>% 
  mutate( phylum=if_else (phylum=="Bacillariophyceae",  "Ochrophyta" , phylum )  ) %>% 
  mutate( kingdom=if_else (phylum=="Ochrophyta",  "Chromista" , kingdom )  ) %>%
mutate( class=if_else (order=="Phaeocystales",  "Prymnesiophyceae" , class )  ) %>% 
  mutate( phylum=if_else (class=="Prymnesiophyceae",  "Haptophyta" , phylum )  ) %>% 
   mutate( kingdom=if_else (phylum=="Ciliophora",  "Chromista" , kingdom )  ) %>% 
  mutate( phylum=if_else (class=="Oomycota",  "Oomycota" , phylum )  ) %>% 
  mutate( kingdom=if_else (class=="Oomycota",  "Chromista" , kingdom )  ) %>% 
  mutate( phylum=if_else (class=="Bigyra",  "Bigyra" , phylum )  ) %>% 
  mutate( kingdom=if_else (class=="Bigyra",  "Chromista" , kingdom )  ) %>% 
mutate( kingdom=if_else (phylum=="Haptista",  "Chromista" , kingdom )  ) %>% 
  mutate( phylum=if_else (class=="Cryptophyceae",  "Cryptophyta" , phylum )  ) %>% 
  mutate( kingdom=if_else (class=="Cryptophyceae",  "Chromista" , kingdom )  ) %>% 
mutate( kingdom=if_else (phylum=="Euglenozoa",  "Protozoa" , kingdom )  )  %>% 
mutate( kingdom=if_else (phylum=="Firmicutes",  "Bacteria" , kingdom )  )  %>% 
mutate( kingdom=if_else (phylum=="Proteobacteria",  "Bacteria" , kingdom )  ) %>% 
  mutate( kingdom=if_else (phylum=="Evosea",  "Protozoa" , kingdom )  ) %>% 
  mutate( kingdom=if_else (phylum=="Euglenozoa",  "Protozoa" , kingdom )  ) %>% 
mutate( phylum=if_else (order=="Macrodasyida",  "Gastrotricha" , phylum )  ) %>% 
  mutate( kingdom=if_else (order=="Macrodasyida",  "Animalia" , kingdom )  ) %>% 
  mutate( phylum=if_else (class=="Acantharea",  "Radiozoa" , phylum )  ) %>% 
  mutate( kingdom=if_else (class=="Acantharea",  "Chromista" , kingdom )  ) %>% 
  mutate( phylum=if_else (class=="Acantharai",  "Radiozoa" , phylum )  ) %>% 
  mutate( kingdom=if_else (class=="Acantharia",  "Chromista" , kingdom )  ) %>% 
mutate( class=if_else (class=="Choanoflagellata",  "Choanoflagellatea" , class )  ) %>% 
mutate( phylum=if_else (class=="Choanoflagellatea",  "Choanozoa" , phylum )  ) %>% 
  mutate( kingdom=if_else (class=="Choanoflagellatea",  "Protozoa" , kingdom )  ) %>% 
mutate( class=if_else (order=="Thaumatomonadida",  "Imbricatea" , class )  ) %>% 
  mutate( phylum=if_else (class=="Imbricatea",  "Cercozoa" , phylum )  ) %>% 
  mutate( class=if_else (class=="Polycystinea",  "Polycystina" , class )  ) %>% 
  mutate( phylum=if_else (class=="Polycystina",  "Radiozoa" , phylum )  ) %>% 
  mutate( kingdom=if_else (class=="Polycystina",  "Chromista" , kingdom )  ) %>%  
  mutate( class=if_else (order=="Leptomyxida",  "Tubulinea" , class )  ) %>% 
  mutate( phylum=if_else (class=="Tubulinea",  "Amoebozoa" , phylum )  ) %>% 
  mutate( kingdom=if_else (class=="Tubulinea",  "Protozoa" , kingdom )  ) %>%  
mutate( kingdom=if_else (phylum=="Discosea",  "Protozoa" , kingdom )  )  %>% 
mutate( kingdom=if_else (phylum=="Tubulinea",  "Protozoa" , kingdom )  )  %>% 
mutate( kingdom=if_else (phylum=="Endomyxa",  "Chromista" , kingdom )  )  %>% 
mutate( kingdom=if_else (phylum=="Cercozoa",  "Chromista" , kingdom )  )  
 ##
 #


```

##  combine_ver_2
```{r combine_ver_2}

dat_match<-dat2 %>% # names(dat2)
  select(lineage, Superkingdom:Species) %>% 
  rename(lineage_orig=lineage) %>% 
  tidyr::unite(lineage_orig_new, Superkingdom:Species, sep=";",remove=F)  %>% 
   inner_join(new2[,c(1,2:9)], by=c("lineage_orig_new"="lineage"))   # names(new)

dat3 <- dat2 %>% # names(dat2)
  select(lineage, Superkingdom:Species,  isMarine:X42) %>% 
  rename(lineage_orig=lineage) %>% 
  tidyr::unite(lineage_orig_corrected, Superkingdom:Species, sep=";",remove=F)  %>% 
  select(lineage_orig, lineage_orig_corrected, isMarine:X42)

  ## fuzzy match ??
dat_match_fuzz<-new2 %>% # names(new2)
  select(lineage, Superkingdom:Species) %>% 
  rename(lineage_good=lineage) %>% 
fuzzyjoin::stringdist_inner_join(dat3, by=c("lineage_good"="lineage_orig_corrected"), max_dist = 25, distance_col = "distance" ) %>% 
  # get closes match only
 group_by(lineage_good) %>%
  top_n(1, desc(distance)) %>%
  ungroup() %>% 
  #filter(distance<5)
  select(lineage_good, lineage_orig_corrected, distance,lineage_orig,  isMarine:X42) %>% 
  #filter(distance>0) %>% 
  arrange(lineage_good, lineage_orig_corrected, distance)
  
  
#  join back to new 2    names(dat_match_fuzz)
new3<-new2 %>% 
    left_join(dat_match_fuzz, by=c("lineage"="lineage_good"))

# export 
data.table::fwrite(new3,paste(dir,share_file,"Red_sea_eDNA_traits_may2021_joined_to_old.csv",sep=""),row.names=F, sep=",")



```



## clean new version

import updated taxa clean it and export it for Tahira
by Nathan updated taxa after improved refernce library - April 2021, done on May 6 2021

```{r clean_new}

dat<- openxlsx::read.xlsx(xlsxFile= paste0(dir,share_file,"Red_sea_eDNA_traits_may2021_joined_to_old_data_added.xlsx")   )

names(dat)

dat1<- dat %>% # names(dat1)
    select(lineage:Species, isMarine, AS_catagory:Planktonic.larval.form, tropic.reference:larvel.reference)


# clean
dat2<-dat1 %>% 
    mutate(trophic.level=ifelse(lineage== "Eukaryota;Fungi;Ascomycota;Dothideomycetes;Pleosporales;Phaeosphaeriaceae;Ophiosphaerella;Ophiosphaerella herpotricha", "detritovore", trophic.level) )  %>% 
    mutate(trophic.level=ifelse(lineage== "Eukaryota;Fungi;Ascomycota;Dothideomycetes;Pleosporales;Didymellaceae;Boeremia;Boeremia exigua", "detritovore" , trophic.level) )  %>% 
   mutate(trophic.level=ifelse(lineage== "Eukaryota;Fungi;Ascomycota;Dothideomycetes;Dothideales;Saccotheciaceae;NA;NA","detritovore"  , trophic.level) )  %>% 
    mutate(trophic.level=ifelse(lineage== "Eukaryota;Fungi;Ascomycota;Dothideomycetes;Dothideales;Saccotheciaceae;NA;NA" , "parasite"   , trophic.level) )  %>% 
    mutate(zone=ifelse(Order=="Archigregarinorida", "benthic" , zone) )  %>% 
    mutate(zone=ifelse(Class=="Spirotrichea", NA , zone) )  %>% 
  mutate(zone=ifelse(Order=="Proseriata", "benthic" , zone) )  %>% 
   mutate(zone=ifelse(Order=="Eugregarinorida", "benthic" , zone) )  %>% 
  mutate(zone=ifelse(Family=="Macrostomidae", "benthic" , zone) )  %>% 
    mutate(zone=ifelse(Order=="Proseriata", "benthic" , zone) )  %>% 
    mutate(zone=ifelse(Order=="Polycladida", "benthic" , zone) )  %>% 
  mutate(zone=ifelse(Order=="Proseriata", "benthic" , zone) )  %>% 
     mutate(zone=ifelse(Order=="Eucoccidiorida", NA , zone) )  %>% 
       mutate(zone=ifelse(Order=="Rotaliida", "benthic" , zone) )  %>% 
      mutate(zone=ifelse(Order=="Eugregarinorida", "benthic" , zone) )  %>%
  mutate(zone=ifelse(Order=="Dolichomicrostomida", NA , zone) )  %>% 
  	mutate(zone=ifelse(Order=="Golfingiida", "benthic" , zone) )  %>%
	mutate(zone=ifelse(Order=="Thraustochytrida", "benthic" , zone) )  %>%
  mutate(Planktonic.larval.form=ifelse(Planktonic.larval.form=="both", "yes" , Planktonic.larval.form) )  %>%
  
  mutate(AS_catagory=ifelse(lineage=="Eukaryota;Animalia;Arthropoda;Hexanauplia;Cyclopoida;Sapphirinidae;Sapphirina;NA", "meso" , AS_catagory) )  %>%	
  mutate(zone=ifelse(lineage=="Eukaryota;Animalia;Arthropoda;Hexanauplia;Cyclopoida;Sapphirinidae;Sapphirina;NA", "planktonic" , zone) )  %>%	

  mutate(trophic.level=ifelse(lineage=="Eukaryota;Animalia;Annelida;Polychaeta;Phyllodocida;Aphroditidae;NA;NA", "deposit feeder", trophic.level) )%>% 

# combine
    #parasite and pathogen
  mutate(trophic.level=ifelse(trophic.level=="parasite" | trophic.level=="pathogen", "parasite/pathogen"   , trophic.level) )  %>% 
   mutate(trophic.level=ifelse(trophic.level=="detritivore" | trophic.level=="deposit feeders", "detritivore/deposit feeder"   , trophic.level) )  %>% 
     # For Zone we put pelagic into planktonic- and intertidal into benthic- We remove any taxa with "land"
    mutate(zone=ifelse(zone=="pelagic", "planktonic" , zone) )  %>% 
    mutate(zone=ifelse(zone=="intertidal", "benthic" , zone) )  %>% 
    filter(zone != "land") 
    
  
mes<-dat2 %>% 
    #filter(Kingdom=="Fungi")
    #filter(trophic.level=="epiphyte/ endophyte")
    #filter(zone=="parasite")
filter(Planktonic.larval.form=="both")


# export 
data.table::fwrite(dat2,paste(dir,share_file,"Red_sea_eDNA_traits_may2021_for_Tahira.csv",sep=""),row.names=F, sep=",")



```














